\section{Foreword}
\label{sec:foreword}

\hspace{1cm} We would like to give our most sincere thanks to Mrs. Tran Thi Thao Nhi and Mrs. Phan Thi Phuong Uyen for this opportunity to do the project. Your valuable advice and encouragement during the course of our work mean a great deal to us, and we cannot appreciate enough the time and effort you have devoted to making us successful. We hope that our results satisfy your expectations.

\vspace{0.5cm}

\hspace{1cm} Although the project is not without its limitations, such as one of our team members being unable to contribute due to his personal circumstances, we have done our best to complete it. We would appreciate your understanding of our situation and the effort we have put into overcoming these challenges.

\vspace{0.5cm}

\hspace{1cm} We really do hope you will like the project and that it lives up to your vision. Your valued comments and feedback will go a long way in our growth and service improvement in the future.

\vspace{0.5cm}

\hspace{1cm} We are particularly very lucky to have been in this project for experience and learning. Any shortcomings and mistakes are solely our own liability, and we take this as an opportunity to improve our skill and knowledge further.

\vspace{0.5cm}

\hspace{1cm} Thank you once more for sparing your valuable time and considering our request. It was an honor and a pleasure working under your guidance, and we hope that someday in life, we get to work with you again.

\vspace{0.5cm}

\hspace{1cm} Best regards,

% ------------------- THE END ------------------- %